---
title: "Introduction to SC19085"
author: "Jinming Liu"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to SC19085}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Overview

__SC19085__ is a simple R package developed to compare the performance of R and R++ (implemented through the R package _Rcpp_) for the 'Statistical Computing' course. Three functions are considered, namely, _rw_Metro_ (generate random nubers using random walk Metropolis sampler); _Jaco_ (calculate the eigenvalues and orthonormal eigenvectors for symmetric matrix using Jacobian method); _iter_thresh_ (estimate the largest(absolute) eigenvalue and the corresponding unit eigenvector for a matrix). For each function, both R and Rcpp versions are produced. Namely _rw_Metro_R_, _Jaco_R_ and  _iter_thresh_R_ for R and _rw_Metro_C_, _Jaco_C_ and _iter_thresh_C_ for C++.

The R package 'microbenchmark' can be used to benchmark the above R and C++ functions.

## Benchmarking _rw_Metro_R_ and _rw_Metro_C_

The Cpp version of random walk metropolis **rw_Metro_C** is as follows:

```{r, eval=FALSE}

  List rw_Metro_C(double sigma, double x0, int N, Function f) {
  
  NumericVector x(N);
  
  NumericVector u = runif(N,0,1);
  
  x[0]=x0;
  
  int k=0;
  
  
  for(int i=1;i<N;i++){
    
    double y= as<double>(rnorm(1,x[i-1],sigma));
    double t1=as<double>(f(y));
    double t2=as<double>(f(x[i-1]));
    
    if(u[i]<= t1/t2){
      x[i]=y;}
    else {
      x[i] = x[i-1];
      k++;
    }
  }
  
  return List::create(
    _["x"] = x, 
    _["k"] = k,
    _["acceptance_rate"]= (double)(N-1-k)/(N-1)
  );
}

```

In order to empirically benchmark _rw_Metro_R_ and _rw_Metro_C_, one need to specify the initial points **x0**, the standard deviation of the random increment **sigma**, the total numbers of replicates **N**, and the target density function **f**. Take the standard Laplace ditribution as an example, the R code for benchmark _rw_Metro_R_ and _rw_Metro_C_ is as follows:

```{r,eval=TRUE}
library(SC19085)
library(microbenchmark)
sigma<-2
x0<-5
N<-1000
f<-function(x) return(0.5*exp(-abs(x)))

 tm1 <- microbenchmark::microbenchmark(
   rwR = rw_Metro_R(sigma,x0,N,f),
   rwC = rw_Metro_C(sigma,x0,N)
   )
 
 print(summary(tm1)[,c(1,3,5,6)])
```


## Benchmarking _Jaco_R_ and _Jaco_C_

The Cpp version of Jacobian method **Jaco_C** is as follows:

```{r, eval=FALSE}

List Jaco_C(MatrixXd A,double tol){
  //Environment base("package:base");
  //Function atan=base["atan"];
  //Function isSymmetric=global["isSymmetric"];
  //Function stop=global["stop"];
  
  //stopifnot(isSymmetric(A));
 
  int n = A.rows();
  MatrixXd V = MatrixXd::Identity(n,n);
  MatrixXd D = MatrixXd::Identity(n,n);
  MatrixXd U;
 
  double maxpq=0.0,phi;
  int p,q;
  
  for(int i=0;i<n-1;i++){
    for( int j=i+1;j<n;j++){
      if(abs(A(i,j))>abs(maxpq)){
        maxpq=A(i,j);
         p=i;
         q=j;
      }
    }
  }

  while (abs(maxpq)>tol){
 
    maxpq=0;
    phi=0.5*atan2(2*A(p,q),A(p,p)-A(q,q));
    
    U = MatrixXd::Identity(n,n);
    U(p,p)=cos(phi);
    U(q,q)=cos(phi);
    U(p,q)=-sin(phi);
    U(q,p)=sin(phi);
    D=U.transpose()*A*U;
    V=V*U;
    A=D;
    
    for(int i=0;i<n-1;i++){
      for(int j=i+1;j<n;j++){
        if(abs(A(i,j))>abs(maxpq)){
          maxpq=A(i,j);
          p=i;
          q=j;
        }
      }
    }
    
  
  }
  VectorXd values = A.diagonal();
  return List::create(
    _["values"] = values, 
    _["vectors"] = V
  );
  
}

```


In order to empirically benchmark _Jaco_R_ and _Jaco_C_, one need to specify the symmetric matrix **A** and the tolerance of error (default value is .Machine$double.eps^0.25), The R code for benchmarking _Jaco_R_ and _Jaco_C_ is as follows.

```{r,eval=TRUE}

A<-matrix(runif(100),nrow=10)
for(i in 1:9){
for(j in (i+1):10) A[i,j]<-A[j,i]
 }
JR <- Jaco_R(A,1e-5)
JR$values
eigen(A)$values

```


## Benchmarking _iter_thresh_R_ and _iter_thresh_C_

The Cpp version of iterative threshold method **iter_thresh_C** is as follows:

```{r, eval=FALSE}

List iter_thresh_C(MatrixXd S,MatrixXd u0,double theta=0.1,
                   double tol=1e-4) {
  
  MatrixXd u_old = u0;
  
  MatrixXd t = S*u_old;
  
  int N = S.rows();
  
  for(int i = 0; i<N ;i++){
    if(abs(t(i,0))<theta) t(i,0) = 0;
  }
  
  double norm = t.norm();
  
  MatrixXd u_new = t/norm;
  
  int k=1;
  double loss = (u_new-u_old).norm();
  
  while(loss>tol){
    cout<<"iteration:"<< k <<" "<<"loss is:"<< loss <<endl;
    u_old=u_new;
    t=S*u_old;
    for(int i=0; i<N ;i++){
      if(abs(t(i,0))<theta) t(i,0)=0;
    }
    norm=t.norm();
    u_new=t/norm;
    k=k+1;
    loss = (u_new-u_old).norm();
  }
  
 VectorXd eigenvalue = u_new.transpose()*S*u_new;
  
  return List::create(
    _["eigen_vector"] = u_new, 
    _["eigen_value"] = eigenvalue
  );
  
}
```

In order to empirically benchmark _iter_thresh_R_ and _iter_thresh_C_
, one need to specify a nxn matrix **S**, the initial eigen_vector(a nx1 matrix) **u0**, sparsity parameter **theta** and the tolerance of error (default value is 1e-4), The R code for benchmarking _iter_thresh_R_ and _iter_thresh_C_ is as follows.

```{r,eval=TRUE}

S<-matrix(runif(400),nrow=20)
S<-t(S)%*%S
u0<-matrix(c(rep(0,19),1))
ITR <- iter_thresh_R(S,u=u0)
ITR
eigen(S)$values[1]

```
